Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-16 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
There was a comment inside the text
Reviewing English grammar from abstract. Couple of changes and proposal for dividing a sentence

\begin{abstract}
Volunteer computing is extensively used in science and industry, but
it still has a long way to go in order to become a mainstream
technology in the same way the cloud technologies in general are. %I
have changed "have" to "are" The lack of general purpose and open
source tools with built-in analytics could be one of the reasons of
why this is so, as well as the lack of proofs of concept. That is why
in this paper we present {\sf NodIO}, a framework used to create
client-server architectures for distributed evolutionary algorithms,
entirely written in JavaScript, which needs minimal server support to
work and that is able to support persistent, asynchronous, distributed
evolutionary algorithms running in the browser, as well as any other
client consuming its REST application programming interface. An
enhanced implementation, which we have called {\sf NodIO-W$^2$}, is
also presented; this version leverages the HTML5 Web Workers
specification to execute several clients per browser and do it in the
background, so that the the number of generations per user could be
improved. The architecture, along with some initial results on the
expected performance and scaling behavior when the number of users is
increased is presented. We also use the algorithm data to find out
what kind of patterns the user behavior follows by examining the
resources they devote to our experiment, and try to fit them to some
statistical distribution to create the bases of a model of user
behavior in volunteer computing experiments of this kind that can be
used by researchers to predict its performance.  In general, our
experiments prove, first, that {\sf NodIO} is a flexible and
low-overhead platform to perform distributed computation experiments
that include volunteers, and then that user behavior follows some
patterns, and, thus, are amenable to a model.
\end{abstract}

>>>>

\begin{abstract}
Volunteer computing is extensively used in science and industry, but
it still has a long way to go in order to become a mainstream
technology in the same way the cloud technologies in general are. %I have changed "have" to "are"
The lack of general purpose and open
source tools with built-in analytics could be one of the reasons of
why this is so, as well as the lack of proofs of concept.
% (Paloma) The following sentence is way too long, and the "which" after "Javascript" is confusing, so one does not know if the which refers to the framework or Javascript by reading the whole sentence.
% I propose: "That is why in this paper we present NodIO, a framework used to create client-server architectures for distributed evolutionary algorithms, entirely written in JavaScript. Our framework needs minimal server support to work and is able to support persistent, asynchronous, distributed evolutionary algorithms running in the browser, as well as any other client consuming its REST application programming interface."
That is why
in this paper we present {\sf NodIO}, a framework used to create
client-server architectures for distributed evolutionary algorithms,
entirely written in JavaScript, which needs minimal server support to
work and that is able to support persistent, asynchronous, distributed
evolutionary algorithms running in the browser, as well as any other
client consuming its REST application programming interface. An
enhanced implementation, which we have called {\sf NodIO-W$^2$}, is
also presented; this version leverages the HTML5 Web Workers
specification to execute several clients per browser and do it in the
background, so that the the number of generations per user could be
improved. The architecture, along with some initial results on the
expected performance and scaling behavior when the number of users is
increased is introduced. % (Paloma) I've changed this "presented" for a synonym
We also use the algorithm data to find out
what kind of patterns the user behavior follows by examining the
resources they devote to our experiment, and try to fit them in % (Paloma) Changed. Phrasal verb was wrong.
 some
statistical distribution to create the bases of a model of user
behavior in volunteer computing experiments of this kind that can be
used by researchers to predict their performance. %(Paloma) Changed to "their" because of "experiments"
In general, our
experiments prove, first, that {\sf NodIO} is a flexible and
low-overhead platform to perform distributed computation experiments
that include volunteers, and then that user behavior follows some
patterns, and, thus, are amenable to a model.
\end{abstract}
